Title of the document here

### 2015-02-05 rmtw/assignment_1/assignment_1.tex
Meth

The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}
%------------------------------------------------------------------------- 
\Section{Methodology}

* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
and investigation methods that  will  be  used  for the study.  Motivate  your  
choice  of  survey/questionnaire  using relevant  references.
* Describe  data  collection  procedures, sampling  method(s),  number  of  
subjects, response  rate  etc.
* Create  questions for your  survey  (include  the questions in  your  report)
* Describe  the population  and size  of  population
* Describe  and motive  method  for analyzing the data
* Discuss validity  threats

%-------------------------------------------------------------------------

\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).

@@

>>>>

The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant. The dependent variable in this example will be the readability of the language.
\newline

@@

%------------------------------------------------------------------------- 
\Section{Methodology}
The main purpose of this study is to discover differences in the perceived readability of code. The study will be carried out in three phases. In phase 1, we will identify the target population. In phase 2, the survey will be designed and carried out. In phase 3, the results of the survey will be analysed. The investigation method will be in the form of a questionnaire. The main argument for the questionnaire is that the survey must be distributed to a large amount of people. A quantitative is also well-suited for this study since there are no existing publications that explore readability differences between languages.

\SubSection{Identifying the Population}
As mentioned before, the goal of this study is to identify the inherent differences in readability of programming languages. To research this, a broad population is required, to avoid results influenced by a possible correlation between the perception of readability and the previously defined independent variables. As such, a research survey has been conducted. This reasoning is reinforced by Easterbrook et al. \cite{easterbrook2008selecting} who state ``Survey research is used to identify the characteristics of a broad population of individuals''. 
\newline

The population of this survey is the students of the Software Engineering and Management programme (SEM) at Gothenburg University. The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language. The SEM program was chosen due to it being accessible for the researchers. 
\newline

\SubSection{Questionnaire Design}
TODO: 
Write briefly about why we chose the languages we chose. (different paradigms etc)
Write some formal stuff about how the survey was designed. (Shit about open-ended questions etc.)
Write which tool was used etc.

Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years):::::
Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three year's.

\SubSection{Results Analysis}
TODO:
* Describe  and motive  method  for analyzing the data

\SubSection{Threats to Validity}
Bias in languages and experience

@@

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}
